Adaptive Global Optimization Based on Nested Dimensionality Reduction\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}

### 2019-03-19 2019/WCGO/WCGO.tex
Final!

\begin{document}
%
\title{Adaptive Global Bptimization Based on Nested Dimensionality 
Reduction\thanks{This study was supported by the Russian Science Foundation, 
project No.\,16-11-10150.}}
%
\titlerunning{Adaptive Global Optimization}
% If the paper title is too long for the running head, you can set 
% an abbreviated paper title here
%
\author{Konstantin Barkalov %\orcidID{0000-0001-5273-2471}  
\and Ilya Lebedev %\orcidID{0000-0002-8736-0652}
}
%
\authorrunning{K. Barkalov, I. Lebedev}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, 
Russia \email{konstantin.barkalov@itmm.unn.ru}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}

>>>>

\begin{document}
%
\title{Adaptive Global Optimization Based on Nested Dimensionality 
Reduction\thanks{This study was supported by the Russian Science Foundation, 
project No.\,16-11-10150.}}
%
\titlerunning{Adaptive Global Optimization}
% If the paper title is too long for the running head, you can set 
% an abbreviated paper title here
%
\author{Konstantin Barkalov %\orcidID{0000-0001-5273-2471}  
\and Ilya Lebedev %\orcidID{0000-0002-8736-0652}
}
%
\authorrunning{K. Barkalov, I. Lebedev}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, 
Russia \email{konstantin.barkalov@itmm.unn.ru}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
